cardinalR: Generating interesting high-dimensional data structures

### 2025-08-23 paper-cardinalR.Rmd
Added branch data

```{r, eval=FALSE}
langevitour::langevitour(expbranches)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(linearbranches)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(curvybranches)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(orglinearbranches)
```

@@

```{r, eval=FALSE}
langevitour::langevitour(orgcurvybranches)
```

@@

```{r branch-proj, fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=15, fig.height=25}

>>>>

```{r}
expbranches_lang <- langevitour::langevitour(expbranches, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
linearbranches_lang <- langevitour::langevitour(linearbranches, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
curvybranches_lang <- langevitour::langevitour(curvybranches, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
orglinearbranches_lang <- langevitour::langevitour(orglinearbranches, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r}
orgcurvybranches_lang <- langevitour::langevitour(orgcurvybranches, levelColors = "black", enableControls = FALSE, width = "500px", height = "400px")
```

@@

```{r branch, eval=knitr::is_html_output(), fig.cap="`langevitour` output  of the `expbranches`, `linearbranches`, `curvybranches`, `orglinearbranches`, and `orgcurvybranches` data in $4\\text{-}D$."}

branchfig <- bscols(
  htmltools::div(
    style = "display: grid; grid-template-columns: 1fr 1fr;",
    expbranches_lang, linearbranches_lang, curvybranches_lang, orglinearbranches_lang, orgcurvybranches_lang
  ),
  device = "xs"
)

class(branchfig) <- c(class(branchfig), "htmlwidget")

branchfig
```

```{r branch-proj, eval=knitr::is_latex_output(), fig.cap="Three $2\\text{-}D$ projections from $4\\text{-}D$, for the `expbranches` (a1-a3), `linearbranches` (b1-b3), `curvybranches` (c1-c3), `orglinearbranches` (d1-d3), `orgcurvybranches` (e1-e3) data.", fig.width=15, fig.height=25}
